BurgerTown Presents: Open Adcess

### 2017-04-23 digital-library.tex
Hella revisions

Fake download buttons are a staple of modern download websites. They really class up the web. Reifying, elegizing, and idealizing nature, these abstract forms with rococo garnishes direct the downloader's attention away from the url to the ad-serving service to which the button points. A deceptive d\'{e}tournement, the premonitory placement of these blissed-out buttons challenges browsers to consider whether they really want to download the paper -- they could, after all, not pursue their line of inquiry and instead watch it evolve vicariously -- which cuts down on the ACM's hosting costs.

By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression. Some regulators have questioned this practice. But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J. Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good. But you still shouldn't eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically. It should be impossible for consumers to access independent, third-party statistics about menu items. ``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them. We don't want the government treating them like dotards," Gary Cohn said to the lobbyists who inform and engage him.}.

@@

To subvert ad blockers, the ad content will be natively hosted on the ACM
digital library as well.
Therefore, ad blockers will be unable to determine which requests are ad
related.

Lastly, we are revolutionizing the fake download practice by dynamically
randomizing the position of the actual download button.
Like serving ad content natively, this will make ad blockers functionally
useless as there will be no way to differentiate between ad content and ACM
content, providing users with instruction on the contingency of fate.
Moreover, this randomization makes it much harder for the user to learn the
positioning of the ads and therefore we hope to drive more clicks to our ad
partners and generate more revenue for the ACM.

\subsection{Rate Limited Free Downloads}
\label{sec:limit}
Free download sites figured out long ago that you can make people pay for an
otherwise free product by making the process of obtaining that free product
difficult.
Therefore, we will split our digital library downloads into two tiers, the free
tier and the \premium tier.

The free tier will only allow downloads at slow speeds and no more than one
paper per day.
Additionally, the user will be required to stare at a screen compelling them to
upgrade while a counter decrements for 10 minutes before the download button is
clickable.
If the engagement of the user---monitored via gaze tracker and wearable heart-rate monitor---falls below the zone of synergy, the counter will be restarted.
The \premium tier will allow unlimited downloads and will not be rate limited.

@@

Additionally, users will not question the presence of captchas on the digital
library as they have already been conditioned to fill captchas for all sorts of
free services.
As such, we do not believe that our user base will know that the ACM is
slinging captcha solutions on the side.

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the user's desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM Digital Library toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

@@

\subsection{Impact Factor-ometer}

@@

Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer. As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}

\begin{figure}
  \centering
  %https://archive.org/details/414803main_0203243
  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
  \caption{A model-year 1985 Noisome-ter, prized by collectors for its muted design that limns adumbrations of sound. The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
  \label{fig:noiseometer}
\end{figure}

>>>>

Fake download buttons are a staple of modern download websites. They really
class up the web. Reifying, elegizing, and idealizing nature, these abstract
forms  direct the downloader's attention away from the url
to the ad-serving service to which the button points. A deceptive
d\'{e}tournement, the placement of these blissed-out buttons
challenges browsers to consider whether they really want to download the paper.
They could, after all, choose to abandon their line of inquiry and instead
watch their field's evolution vicariously through mainstream media, which cuts
down on the ACM's hosting costs.

By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression. Some regulators have questioned this practice. But we
believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of
  the National Economic Council, stressed in an interview with \textit{The Wall
Street Journal} compared a website without fake-download buttons to the menu at
P.J. Bland's: ``This is like putting only health food on the menu, because
unhealthy food tastes good. But you still shouldn't eat it because you might
die younger." The menus of a free society, in his reckoning, should include
both unhealthy and healthy items, and they should be labeled and priced
identically. It should be impossible for consumers to access independent,
third-party statistics about menu items. ``We believe our customers are
informed and engaged, and we trust that they are smart enough to make the
decisions that are right for them. We don't want the government treating them
like dotards," Gary Cohn said while spraying an unlabeled can of spray cheese
into his mouth.}.

@@

To subvert ad blockers, the ad content will be natively hosted on the ACM
digital library as well.
Therefore, ad blockers will be unable to determine which requests are ad-related.

Additionally, we are revolutionizing the fake download practice by dynamically
randomizing the position of the actual download button.
Like serving ad content natively, this will make ad blockers functionally
useless as there will be no way to differentiate between ad content and ACM
content, providing users with instruction on the contingency of fate.
Moreover, this randomization makes it much harder for the user to learn the
positioning of the ads and therefore we hope to drive more clicks to our ad
partners and generate more revenue for the ACM.

Lastly, we are working on a proposal that will greatly reduce ACM hosting
costs, namely we  will replace the only real download button with a fake one.

\subsection{Rate-Limited Free Downloads}
\label{sec:limit}
Free download sites figured out long ago that you can make people pay for an
otherwise free product by making the process of obtaining that free product
difficult.
Therefore, we will split our digital library downloads into two tiers, the free
tier and the \premium tier.

The free tier will only allow downloads at slow speeds and no more than one
paper per day.
Additionally, the user will be required to stare at a screen compelling them to
upgrade while a counter decrements for 10 minutes before the download button is
clickable.
If the engagement of the user---monitored via gaze tracker and wearable
heart-rate monitor---falls below the Zone of Synergy\texttrademark, the counter will be restarted.
The \premium tier will allow unlimited downloads along with an upgraded
experience: the countdown clock will have ads replaced by a sponsored message
thanking you for upgrading and will feature a \premium digital clock face.

@@

Users will not question the presence of captchas on the digital
library as they have already been conditioned to fill captchas for all sorts of
free services.
As such, we do not believe that our user base will know that the ACM is
slinging captcha solutions on the side.

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the user's desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM Digital Library toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will provide this information to our partners for a nominal fee who may use
this user data to curate a product-based lifestyle that will make our readers' lives
more relevant to advertisers.

@@

\subsection{Impact Factometer}

@@

Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman,
Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's
historic Wrigley Field to make use of the stadium's native Noiseometer. As Pat
Hughes reads the papers over the PA , the council---taking especial care to
note the presence of key phrases like ``cross-promotional deal mechanics
revenue streams jargon synergy" and ``a strategic planning initiative\ldots
with a focus on strategic dynamism"---emits cheers in proportion to its
perception of the paper's impact, and these cheers are registered on the
Noiseometer, which assigns metrics of impact to each paper, as shown in Figure~\ref{fig:noiseometer}

\begin{figure}
  \centering
  %https://archive.org/details/414803main_0203243
  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpeg}
  \caption{A model-year 1985 Noiseometer, prized by collectors for its muted
  design that limns adumbrations of sound. The paper in which these meetings
were proposed was met at the first such convening of the Council with a cheer
so loud it registered a ``Nowhere Permissible Voice" \todo{maybe think of
something better} (not shown) on this scale.}
  \label{fig:noiseometer}
\end{figure}

### 2017-04-23 future-work.tex
Hella revisions

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in exchange for their continued appreciation of the
safe practices within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

>>>>

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in case of a surprise inspection in exchange for
their continued appreciation of the safe practices within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

### 2017-04-23 introduction.tex
a couple small modifications to three files
Hella revisions

\section{Introduction}
Open access is a movement to make papers and other research contributions
freely accessible to the general public \cite{oa}.
The ACM has been working for some time to achieve the open access dream but
have found this dream to be prohibitively expensive.
As such, we have required authors to opt-in to open access by paying the cost
themselves \cite{auth}.
However, we have found a way to provide open access papers at no cost to the
authors by adopting the techniques employed by various websites and
publications that manage to distribute content for free.

Section~\ref{sec:related} details techniques used by other services to achieve
free downloads and paper distribution.
Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
bring it up to the current standards for download portals.
Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that
the papers themselves are profitable.
Section~\ref{sec:future} provides work from a future that directly results from the present work.

>>>>

\section{Introduction}
Open access is a movement to make papers and other research contributions
freely accessible to the general public \cite{oa}.
The ACM has been working for some time to achieve the open access dream but
has found this dream to be prohibitively expensive.
As such, we have required authors to opt-in to open access by paying the cost
themselves \cite{auth}.
However, we have found a way to provide open access papers at no cost to the
authors by adopting the techniques employed by various websites and
publications that manage to distribute content for free.

Section~\ref{sec:related} details techniques used by other services to achieve
free downloads and paper distribution.
Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
bring it up to the current standards for download portals.
Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that
the papers themselves are profitable.
Section~\ref{sec:future} provides work from a future that directly results from
a present that includes the present work.

### 2017-04-23 openadcess.tex
Compiles
Hella revisions

@@

>>>>

\authorinfo{Brett Boston}{Institute for Clarity in Documentation}{boston@csail.mit.edu}
\authorinfo{Max Dunitz}{Institute with Document Obfuscation}{mdunitz@alum.mit.edu}

@@

\section*{Acknowledgements}
This research was funded through sales of counterfeit reprints of papers.
To keep costs low we don't pay for the original copy, we write a new article
based on the abstract and pass the savings on to us!

### 2017-04-23 paper-sponsorships.tex
Hella revisions

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.\footnote{Wisdom disputes this claim, but we have the narrow computational tools to prove our publication and community have way more holism.}
Our readership is mostly devoid of energy vampires and is therefore suitable
for empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

\subsection{Banner ads}
Web surfers today have become accustom to seeing banner ads on their favorite
websites.
Therefore, we will be incorporating these advertisements into all of our
papers.
Advertisements can be easily inserted into existing \LaTeX\ papers through the
use of the \texttt{\textbackslash figure} and \texttt{\textbackslash figure*}
constructs.
Of course, advertisements using the two column \texttt{\textbackslash figure*}
construct will be considerably more expensive than their one column brethren.
A standard single column ad can be seen in \autoref{fig:law} while a
double-wide can be found in \autoref{fig:usa}.

@@

For an additional fee we will also allow advertisers to embed autoplaying audio
into their paper ads.
While we aren't currently sure whether or not the PDF specification allows
this, we believe that there are sufficiently many ACM loving PhDs at Adobe to
get this change  pushed into the spec.

\subsection{Ad Enhanced Fonts}
Computer Modern is a staple of today's papers, but we believe that this font can
be monetized.
By replacing the characters in the default \LaTeX\ font with corporate logos
we can convey the same information in an ad enhanced way. The inspiring example of Claude Shannon proves it!

During each call for papers we will also put out a simultaneous call for
logos where companies can bid on desirable letters.
To avoid a Wingdings situation \cite{wingdings}, we require that the company
logo is a stylized version of the letter being replaced.

\subsection{Native Ads}
Native advertisements are advertisements meant to be disguised among the normal
content of a publication.
They are written in the same style as the publication and appear alongside
unsponsored content in an attempt to make the reader believe that they are
reading the original publication and not an advertisement \cite{native}.

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads must be indistinguishable from the rest of the paper, an
advertisement that is recognizable as an ad will result in the rejection of the
paper.
The ad section must be at least one page long, but there is no upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

@@

We are excited to announce that our first partner in this endeavor will be
Chili's Grill \& Bar,\footnote{Pronounced: ``Kill me's'' The chill of severity and emptiness.} who has purchased the rights to the set of natural
numbers.
From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
Natural Numbers \(\mathbb{N}\).

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect.
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the offending authors.

@@

What of the science that does get published? The agents who do get economically controversial results published---the humble, modest, yeoman-scientist free agents---are likely to be powerful entities in a society with concentrated private economic power, some argue. How is that democratic? Well, Madison got it right. It's not only democratic, it's the purest form of democracy: the ``mischief of the factions." Simply put, ISDS provides a powerful mechanism of checks and balances. If Hot Packets wants to get their signature snack food placed on the government's food pyramid, it would need peer-reviewed science attesting to its beneficial health effects (such as an appearance on the Doctor Conflict-of-Interest show, where the titular doctor attests to its miracle superfood status, or a research paper). To appear in print, it would have to pay off claims from competing superfoods such as Berry Loops or Jazz Flakes. The system works! But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and questioning Robinsonian labor market monopsony would have little trouble passing ISDS. Approved ideas get approved quickly, and the system works!

@@

  \item I was hiding in your closet at 54 Bishop Allen Dr. \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
\end{enumerate}

@@

\subsection{Check Scams}

Digital is the new normal. Digital is the new ubiquity. Digital is the new cuddling. Digital is the new word we use to paper over our alienation with the capitalist mode of production at a time when socialism is possible.

@@

But an author need not remain ensconced in the stately pleasure-dome of digital. In fact, when an author chooses to transact in the physical space, the open-adcess model empowers the author to not only avoid paying the publishing fee but also to get on the road to getting paid for their articles because authors deserve more. Recent accounting innovations surveyed in two review articles and one major motion picture ["Consumer Information: Fake Checks"
https://www.consumer.ftc.gov/articles/0159-fake-checks; "Counterfeit Check
Scams: CONSUMER ALERT" http://www.michigan.gov/ag/0,4534,7-164-17337\_20942-176356--,00.html; \textit{Bridget Jones's Check Scam} distributed by Universal Pictures] enable the ACM to write large checks to authors. In return, authors simply have to write a small check to cover transaction fees before the large check clears.

>>>>

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.\footnote{Wisdom disputes this claim, but we have the narrow computational tools to prove our publication and community have way more holism.}
Our readership is mostly devoid of energy vampires and is therefore suitable
for empath advertisers.
Where IEEE uses Western proof verification techniques, our broad-minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

\subsection{Banner ads}
Web surfers today have become accustomed to seeing banner ads on their favorite
websites.
Therefore, we will be incorporating these advertisements into all of our
papers.
Advertisements can be easily inserted into existing \LaTeX\ papers through the
use of the \texttt{\textbackslash figure} and \texttt{\textbackslash figure*}
constructs.
Of course, advertisements using the two-column \texttt{\textbackslash figure*}
construct will be considerably more expensive than their one-column brethren.
A standard single-column ad can be seen in \autoref{fig:law} while a
double-wide can be found in \autoref{fig:usa}.

@@

For an additional fee we will also allow advertisers to embed autoplaying audio
into their paper ads.
While we aren't currently sure whether or not the PDF specification allows
this, we believe that there are sufficiently many ACM-loving PhDs at Adobe to
get this change  pushed into the spec.

\subsection{Ad-Enhanced Fonts}
Computer Modern is a staple of today's papers, but we believe that this font can
be monetized.
By replacing the characters in the default \LaTeX\ font with corporate logos
we can convey the same information in an ad enhanced way.
%The inspiring example of Claude Shannon proves it!

During each call for papers we will also put out a simultaneous call for
logos where companies can bid on desirable letters.
To avoid a Wingdings thing \cite{wingdings}, we require that the company
logo be a stylized version of the letter being replaced.

\subsection{Native Ads}
Native advertisements are advertisements meant to be disguised among the normal
content of a publication, much the way nutrition is disguised in the
kid-tested, parent-approved, and flavor packed Flavor Paks.
They are written in the same style as the publication and appear alongside
unsponsored content in an attempt to make the reader believe that they are
reading the original publication and not an advertisement \cite{native}.

At paper registration time, authors will be given ad copy\footnote{Beware that
  accessing our site over Tor or other anonymizing networks can result in ad
copy presented in another language.}
  to integrate into their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads must be indistinguishable from the rest of the paper, an
advertisement that is recognizable as an ad will result in the rejection of the
paper.
The ad section must be at least one page long, but there is no upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

@@

We are excited to announce that our first partner in this endeavor will be
Chili's Grill $\|$ Bar,\footnote{The chill of severity and emptiness in every
bite.} which has purchased the rights to the set of natural
numbers.
From here on, authors must refer to this set as the Chill's Grill $\|$ Bar Set of
Natural Numbers \(\mathbb{N}\).

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company, or 25 US Dollars\footnote{In the present, United
  States Dollars are the one true world currency.  The value of \$25
in yesterday's Austro-Hungarian forint is not known.}, whichever is greater.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect\footnote{At least influenza feels like
something.}
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the offending authors.

@@

What of the science that does get published? The agents who do get economically controversial results published are likely to be powerful entities in a society with concentrated private economic power, some argue.
On the contrary, we contend that such restrictions on publication enable the
purest form of democracy, the ``mischief of factions."
Simply put, ISDS provides a powerful mechanism of checks and balances. If Hot
Packets wants to get their signature snack food placed on the government's food
pyramid, it would need peer-reviewed science attesting to its beneficial health
effects (such as an appearance on the Doctor Conflict-of-Interest show, where
the titular doctor attests to its miracle superfood status, or a research
paper). To appear in print, it would have to pay off claims from competing
superfoods such as Berry Loops or Jazz Flakes.
But, say, if the parent companies of all products for sale wish to merge,
research touting the consumer benefits of concentration would have little
trouble passing ISDS review.
 Approved ideas get approved quickly, and the system works!

@@

  \item I was hiding in your closet at 1 Infinite Loop Apt. \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
\end{enumerate}

@@

\subsection{Check Scams}
\iffalse
Digital is the new normal. Digital is the new ubiquity. Digital is the new cuddling. Digital is the new word we use to paper over our alienation with the capitalist mode of production at a time when socialism is possible.

@@

But an author need not remain ensconced in the stately pleasure-dome of digital. In fact, when an author chooses to transact in the physical space, the open-adcess model empowers the author to not only avoid paying the publishing fee but also to get on the road to getting paid for their articles because authors deserve more.
\fi
Recent accounting innovations surveyed in two review articles and one major
motion picture \cite{ftc, check-scams, mich} enable the ACM to write large
checks to authors. In return, authors simply have to write a small check to
cover transaction fees before the large check clears.

### 2017-04-23 related-work.tex
deleted an unnecessary line 'narrow computational tools'
Hella revisions

Rapidshare \cite{rapidshare} was a website that provided rate-limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service. Or maybe they did not take this technique far enough. He he he.

Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.

>>>>

Rapidshare \cite{rapidshare} was a website that provided rate-limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists it seems that this technique, used alone,
is insufficient to cover the costs of running a download service. Or maybe they
did not take this technique far enough\ldots

Wisdom \cite{wisdom} and many other free rags make heavy use of
traditional print ads, native ads, and classifieds,
so that paper copies may be profitably distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.

We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.
